Software Citation Principles

### 2016-07-26 sc-principles/rebuttal/rebuttal.tex

\textbf{Our response:}
We agree that this paper is more of a position paper than research article, and thus that creating a research question would be an artificial construct. We are willing to make this change if required, but feel it wouldn't add much to the paper.

We modeled our process on the work done by the FORCE2016 Data Citation group, which included publishing a \emph{PeerJ CS} paper (\url{https://peerj.com/articles/cs-1/}) which was written in a similar manner to our paper.

\item \textbf{Reviewer comment:}
\emph{The use cases described in Section 3 form the main method to answer the implicit research question. Given the importance of these use cases for this paper, I think reference [18] with the details about these use cases should be published in a more official way, either on a site like ArXiv or FigShare, or maybe even as supplemental material or appendix for this paper. I think having these use cases in the appendix of this paper would be the best solution, which would also increase the impact of these use cases and would strengthen the paper in general.}

\textbf{Our response:}
We agree, and have added the full use cases text (with some edits for clarity and completion) as the new Appendix B for completeness.
We also added the comments (with our responses) made publicly following the presentation of the draft principles document at the FORCE2016 conference, as Appendix C.

@@

\item \textbf{Reviewer comment:}
\emph{As noted above, the logical structure of the paper is unclear, and therefore it is not clear what exactly the main findings are. I think the main findings should be the principles stated in the beginning, and the use cases would then form the main method to arrive at these findings. Alternatively, one could label the principles as ``assumptions'' and apply the use case study to validate these assumptions. In any case, I think the findings are valid but they should be labeled as preliminary, as it is not possible to arrive at a final conclusion for such kinds of questions. Only the future can tell whether software citations really work out.}

\textbf{Our response:}
We agree that the main findings of the paper are the software citation principles, and as described in our response to point 1 above, we have updated the introduction and made some structural changes to make this clear.

However, we respectfully don't agree that the principles are preliminary, but would describe them as reflecting the group's current knowledge and experience.  We agree that ``only the future can tell whether software citations really work out,'' but this is true of most papers: they capture the current state of scientific knowledge in an area.

@@

\item \textbf{Reviewer comment:}
\emph{line 88: ``which will be presented ...'' to ``which was presented ...''}

\textbf{Our response:}
We agree, and have made this change.

\item \textbf{Reviewer comment:}
\emph{line 89: ``We expect that this discussion may lead to a second, final version'': So this paper is not the final version? Please clarify.}

\textbf{Our response:}
Thank you for pointing this error out. We have corrected this statement to indicate that the past discussion led to a second version (what was submitted).

@@

\item \textbf{Reviewer comment:}
\emph{line 97: ``the need for credit for application software underscores the need to overhaul the system of credit for all research products.'': Very true and very important. But then maybe the concept of a ``citation'' is obsolete altogether, and we shouldn't be advocating ``software citations'', but something new altogether? Some more discussion on this would be valuable, I think. This relates to my comment above about a long-term vision.}

\textbf{Our response:}
\asnote{We probably need to dig out some citations about improved/rich citation. I'm aware of some work that was going on in the PLOS Labs group about this but I'm not sure if that work was ever published.}

\niemnote{The idea of citations is not going to go away---but format and how they fit in ecosystem may change.}

\niemnote{Arfon: can you help here?}
\niemnote{I think we have something on this at the end of section 3}

### 2016-07-26 sc-principles/rebuttal/rebuttal.tex

\begin{enumerate}
\item \textbf{Reviewer comment:}
\emph{The logical connections between the different parts of the paper are not clear. For example, how do the ``basic requirements'' of Table 2 map to the ``principles'' in Section 1? And are the principles presented in the beginning the *outcome* of this research (this is what lines 29+ seem to suggest) or are they *assumptions* of the approach to be discussed and evaluated (this is how they seem to be treated in Section 5).}

\textbf{Our response:}
We view the principles presented at the beginning as the main outcomes\slash results of this work, with the process of producing them (discussed in the new Section 3) based on a synthesis of information from the use cases and related work. Then, Section 6 (previously 5) discusses the ``results''.
Our modifications to the structure of the paper, and changes we hope improve the logical flow, should help indicate these connections better.

\item \textbf{Reviewer comment:}
\emph{It is not clear whether the authors consider software citations to be just the first step towards a long-term vision, or whether they consider software citations the overall final solution. It seems that the first is the case, but the long-term vision is not discussed.}

\textbf{Our response:}
Ultimately we believe that software citation is just a part of a more complete solution for the sharing and citation of all of the scholarly research products. We have updated the language in the first paragraph of ``Motivations''

### 2016-07-26 sc-principles/software-citation-principles.tex
fixing spaces around em-dash
(final) wording fix on historical use case
Adding some language about software citations being only a part of a more complete solution for citing research outputs.

As the process of research\footnote{We use the term ``research'' in this document to include work intended to increase human knowledge and benefit society, in science, engineering, humanities, and other areas.} has become increasingly digital, research outputs
and products have grown beyond simply papers and books to include software,
data, and other electronic components such as presentation slides, posters,
(interactive)  graphs, maps, websites (e.g., blogs and forums), and multimedia
(e.g., audio and  video lectures).  Research knowledge is embedded in these
components. And papers and books themselves are also becoming increasingly
digital, allowing them to become executable and reproducible. As we move towards
this future where research is performed in and recorded as a variety of linked
digital products, the characteristics and properties that developed for books
and papers need to be applied to all digital products and possibly adjusted.
Here, we are concerned specifically with the citation of software products. The
challenge is not just the textual citation of software in a paper, but the more
general identification of software used within the research process.

@@

Researcher is engaged in historical/cultural research --- e.g., study of video games as cultural artifacts.

>>>>

As the process of research\footnote{We use the term ``research'' in this document to include work intended to increase human knowledge and benefit society, in science, engineering, humanities, and other areas.} has become increasingly digital, research outputs
and products have grown beyond simply papers and books to include software,
data, and other electronic components such as presentation slides, posters,
(interactive) graphs, maps, websites (e.g., blogs and forums), and multimedia
(e.g., audio and  video lectures).  Research knowledge is embedded in these
components. And papers and books themselves are also becoming increasingly
digital, allowing them to become executable and reproducible. As we move towards
this future where research is performed in and recorded as a variety of linked
digital products, the characteristics and properties that developed for books
and papers need to be applied to all digital products and possibly adjusted.
Here, we are concerned specifically with the citation of software products. The
challenge is not just the textual citation of software in a paper, but the more
general identification of software used within the research process. This work is
focused on making software a citable entity throught the scholarly ecosystem. While
software products are a relatively small fraction of the sum total of
research output, this work together with other efforts such as the Force11
Data Citation Principles~\cite{data-citation-principles} collectively represent
an effort to better describe all the outputs of research.

@@

Researcher is engaged in historical/cultural research, e.g., a study of video games as cultural artifacts.
